Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-28 6-ModelPresentation.tex
replace UML by macro

Figure \ref{fig:BaseMetamodel} represents this base metamodel with a UML-like formalism, well adapted to represent object-oriented FML concepts and their instances. Base conceptual element is called a \textit{FlexoConcept} in FML language, and is similar to the concept of class in object-oriented modeling. The UML representation of class is used to represent a \textit{FlexoConcept}, while cardinalities are shown using the UML-like classical rules. 
In the diagram, we choose to represent the role associated with the \textit{FlexoConcept} in the class square and the role type is referenced by the arrow in front of the role name.

>>>>

Figure \ref{fig:BaseMetamodel} represents this base metamodel with a \UML-like formalism, well adapted to represent object-oriented FML concepts and their instances. Base conceptual element is called a \textit{FlexoConcept} in FML language, and is similar to the concept of class in object-oriented modeling. The \UML representation of class is used to represent a \textit{FlexoConcept}, while cardinalities are shown using the \UML-like classical rules. 
In the diagram, we choose to represent the role associated with the \textit{FlexoConcept} in the class square and the role type is referenced by the arrow in front of the role name.
